CODE CHECK

### 2020-09-16 codecheck-paper.Rmd
Get the .tex output

---
title: "CODE CHECK"
author:
- affiliation: Department of Applied Mathematics and Theoretical Physics, University of Cambridge, Cambridge, Cambridgeshire, GB
  corresponding: sje30@cam.ac.uk
  email: sje30@cam.ac.uk
  name: Stephen Eglen
  orcid: 0000-0001-8607-8025
- affiliation: Institute for Geoinformatics, University of M"unster, M"unster, Germany
  email: daniel.nuest@uni-muenster.de
  name: Daniel Nüst
  orcid: 0000-0002-0024-5046
date: "`r format(Sys.time(), '%d %B, %Y')`"
abstract: |
          | ...
#author_summary: |
#  TBD
bibliography: bibliography.bib
#output: rticles::plos_article
#csl: plos.csl
output: pdf_document
---

@@

# Open questions

* Prefer one sentence per line / short / one para per line.
* Nust* and Eglen*. contributed equally.
* latex.
* Which journal to target -- maybe worry abotu that once we have a
  preprint.  F1000R my current favourite.

* Check with Giuliano re: "code works".  Write to Naomi to apologise / placeholder.

@@

\begin{figure}
  \centering
  \caption{The detective. Could we number the arrows as steps?
(Implementing the CODECHECK process).  DANIEL: best source for this figure?}
  \label{fig:worfklow}
\end{figure}

@@

## Core principles

>>>>

---
title: "CODE CHECK"
author:
- affiliation: Department of Applied Mathematics and Theoretical Physics, University of Cambridge, Cambridge, Cambridgeshire, GB
  corresponding: sje30@cam.ac.uk
  email: sje30@cam.ac.uk
  name: Stephen Eglen
  orcid: 0000-0001-8607-8025
- affiliation: Institute for Geoinformatics, University of M"unster, M"unster, Germany
  email: daniel.nuest@uni-muenster.de
  name: Daniel Nüst
  orcid: 0000-0002-0024-5046
date: "`r format(Sys.time(), '%d %B, %Y')`"
abstract: |
          | ...
#author_summary: |
#  TBD
bibliography: bibliography.bib
#output: rticles::plos_article
#csl: plos.csl
output:
  pdf_document:
    keep_tex: true  
---

@@

# TODO

* Nust* and Eglen*. contributed equally.

* Check with Giuliano re: "code works".  Write to Naomi.

@@

\begin{figure}
  \centering
	  \includegraphics{/home/stephen/papers/talks/talkfigs/openscience/codecheck_overview.pdf}
  \caption{The detective. Could we number the arrows as steps?
(Implementing the CODECHECK process).  DANIEL: best source for this figure?}
  \label{fig:worfklow}
\end{figure}

@@

# Core principles
